Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-09-29 manuscript.Rmd
suggest appendix for wordcount #228

Standards for scientific writing are designed to result in understandable and comprehensive research articles and can serve the same purpose for writing a preregistration.
Standards for scientific writing [e.g. @apa7] require that research articles are described in such detail that any researcher that is familiar with the field is able to repeat a given study.
They provide, hence, an excellent vehicle for planning a study.
One particular advantage is the foundation in existing literature where the introduction and theoretical background provide the basis for the studies' design.
Nevertheless, it can be fruitful to consult preregistration templates because of their strong focus on formulating a comprehensive methods section.
If the PAC is submitted as a registered report [an article format in which the preregistration is reviewed and the article accepted "in principle", @nosekRegisteredReports2014; @chambersWhatNextRegistered2019] a journal article might be more familiar to the reviewers that ensure a comprehensive study plan.

@@

>>>>

Standards for scientific writing are designed to result in understandable and comprehensive research articles and can serve the same purpose for writing a preregistration.
Standards for scientific writing [e.g. @apa7] require that research articles are described in such detail that any researcher that is familiar with the field is able to repeat a given study.
They provide, hence, an excellent vehicle for planning a study.
One particular advantage is the foundation in existing literature where the introduction and theoretical background provide the basis for the studies' design.
Nevertheless, it can be fruitful to consult preregistration templates because of their strong focus on formulating a comprehensive methods section.
One factor that reduces comprehensiveness of such manuscript style but that is absent in standard preregistrations are strict word count limits that some journals impose.
In such case we suggest using appendix materials to keep the manuscript concise, yet the preregistration comprehensive.

@@

Peer review of preregistration is a method that also can ensure comprehensiveness e.g. a registered report [an article format in which the preregistration is reviewed and the article accepted "in principle", @nosekRegisteredReports2014; @chambersWhatNextRegistered2019].
In such registered report peer reviewing a manuscript styled PAC might be more familiar to the reviewers that ensure a comprehensive study plan.
